Simple SIR

### 2018-04-09 SimpleSIR.Rmd
Remove computer specific working directories

```{r}
# tic=Sys.time()
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")

@@

##Plot deterministic and stochastic SIR results (assuming equal mixing)
Compare/verify output from deterministic ODE and stochastic SIR models
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")
#set wd to location of stochastic SIR simulation output files

@@

##Read in file names 
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")
filenames <- list.files(path = "C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")
summaries<-filenames[grep("summary", filenames)] #summary data
infecteds<-filenames[grep("infect", filenames)] #I data

##Make a merged dataset from all available .csv files
SIRdata_merged<- do.call("rbind", lapply(summaries, read.csv, header = TRUE))
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/")
write.csv(SIRdata_merged, file="SIRdata_merged.csv")

@@

##Box plots
Box plots comparing density and recovery rates for homogenous mixing SIR model
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
#sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks

@@

##Fig. S6
Compare homogenous mixing and spatial models in box plot form.
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/")
SIRdata_merged<-read.csv("SIRdata_merged.csv")
SIRdata_merged<-SIRdata_merged[,-1]

@@

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
tiff("FigureS6.tiff", height = 17, width = 17,8, units = "cm", compression = "lzw", res = 1200)
p
#multiplot(hh,ii, cols=1)
dev.off()
```

>>>>

```{r}
# tic=Sys.time()
#setwd()

@@

##Plot deterministic and stochastic SIR results (assuming equal mixing)
Compare/verify output from deterministic ODE and stochastic SIR models
```{r}
setwd()
#set wd to location of stochastic SIR simulation output files

@@

##Read in file names 
#setwd()
filenames <- list.files(path = "") #udpate with file path containing simulation data
summaries<-filenames[grep("summary", filenames)] #summary data
infecteds<-filenames[grep("infect", filenames)] #I data

##Make a merged dataset from all available .csv files
SIRdata_merged<- do.call("rbind", lapply(summaries, read.csv, header = TRUE))
#setwd("")
write.csv(SIRdata_merged, file="SIRdata_merged.csv")

@@

##Box plots
Box plots comparing density and recovery rates for homogenous mixing SIR model
```{r}
#setwd("")
#sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks

@@

##Fig. S6
Compare homogenous mixing and spatial models in box plot form.
```{r}
#setwd() #set working directory to folder containing SIRdata_merged.csv
SIRdata_merged<-read.csv("SIRdata_merged.csv")
SIRdata_merged<-SIRdata_merged[,-1]

@@

#setwd()
tiff("FigureS6.tiff", height = 17, width = 17,8, units = "cm", compression = "lzw", res = 1200)
p
#multiplot(hh,ii, cols=1)
dev.off()
```
